Introducing statistics with \texttt{intRo}

### 2015-02-16 student-paper-competition-2014/paper.Rmd

---
title: "Introducing statistics with \\texttt{intRo}"
author: "Eric Hare & Andee Kaplan"
date: "December 14, 2014"
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    number_sections: yes
bibliography: refs.bib
geometry: margin=0.8in
---
\thispagestyle{empty}

>>>>

---
title: "Introducing statistics with \texttt{intRo}"
author: "Eric Hare & Andee Kaplan"
date: "December 14, 2014"
output:
  pdf_document:
    includes:
      in_header: preamble.tex
    number_sections: yes
  html_document: default
bibliography: refs.bib
geometry: margin=0.8in
---
\thispagestyle{empty}
